\Title

### 2021-01-26 manuscript/manuscript.tex
Use the siunits package
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution
strategy for the ground and airborne synthetic surveys, respectively.
For the synthetic ground survey, the horizontal layouts produced similar RMS
values of appropriately 0.8 mGal regardless of the depth type, with the
exception of the regular-grid layout which produced a larger RMS of
\BestGroundGridSourcesConstantDepthRms{} mGal.
The differences between the target grid and the interpolated values are larger
in regions of poor data coverage.
Edge effects are present for all strategies but are noticeably smaller for the
combination of block-averaged-sources with a variable depth based on the
nearest neighbour distance.
For the synthetic airborne survey, all strategies (including the regular-grid)
produced similar RMS errors of approximately 0.3 mGal.
The maps of the differences between the target grid and interpolation results
are visually indistinguishable from each other.

>>>>

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution
strategy for the ground and airborne synthetic surveys, respectively.
For the synthetic ground survey, the horizontal layouts produced similar RMS
values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
exception of the regular-grid layout which produced a larger RMS of
\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
The differences between the target grid and the interpolated values are larger
in regions of poor data coverage.
Edge effects are present for all strategies but are noticeably smaller for the
combination of block-averaged-sources with a variable depth based on the
nearest neighbour distance.
For the synthetic airborne survey, all strategies (including the regular-grid)
produced similar RMS errors of approximately \SI{0.3}{\mgal}.
The maps of the differences between the target grid and interpolation results
are visually indistinguishable from each other.
